Ideas

### 2023-07-16 Notes.tex
try
some related stuff

\item Does the theory above apply to other cases. E.g., if one wants a
  proper notion of causality (avoiding or-causality) a possibility
  seems to be to restrict the applicability condition for rules, to
  prevent fusions to act on already merged items (see section V.D in
  the arxiv). By the way, note that the satisfaction of the conditions
  on shift depends not only on the notion of shift, but also on the
  notion of rewriting. In this case we expect to have a prime event
  structure (bit this has to do with the second part of the work).

@@

For this part, relevant material is section V of Arxiv. We use abstraction equivalence (iso of derivations) $\equiv^{a}$ (def. 36), shift-equivalence $\shifteq_\sigma$ (Def. 38, traking the permutation) and their join $\equiv^c_\sigma$.

For linear rules on graphs it is known that two derivations are
related by $\rho \equiv^c_\sigma \rho'$ iff $\sigma$ is a consistent
permutation (def. 40, arxiv). Rough;y the idea is to take the colimit
and consider the rewriting steps over the colimit to deduce
dependencies. This was used in many places in the proofs, but for
left-linear rules the proof does not go through (only the implication
``if $\rho \equiv^c_\sigma \rho'$ then $\sigma$ is a consistent
permutation'' (Lemma 17(1)) seems to hold as the original proof do not
to rely on linearity, this should be double-checked, but the converse
is false). In general, the hope is to get rid of using consistent
permutation and use instead more asbtract properties of
shift-equivalence as discussed in the first part.

@@

Relevant technical lemma in Arxiv are:

>>>>

\item Does the theory above apply to other cases. E.g., if one wants a
  proper notion of causality (avoiding or-causality) a possibility
  seems to be to restrict the applicability condition for rules, to
  prevent fusions to act on already merged items (see section V.D in
  UnstableFull). By the way, note that the satisfaction of the conditions
  on shift depends not only on the notion of shift, but also on the
  notion of rewriting. In this case we expect to have a prime event
  structure (bit this has to do with the second part of the work).

@@

For this part, relevant material is section V of UnstableFull. We use abstraction equivalence (iso of derivations) $\equiv^{a}$ (def. 36), shift-equivalence $\shifteq_\sigma$ (Def. 38, traking the permutation) and their join $\equiv^c_\sigma$.

For linear rules on graphs it is known that two derivations are
related by $\rho \equiv^c_\sigma \rho'$ iff $\sigma$ is a consistent
permutation (def. 40, UnstableFull). Rough;y the idea is to take the colimit
and consider the rewriting steps over the colimit to deduce
dependencies. This was used in many places in the proofs, but for
left-linear rules the proof does not go through (only the implication
``if $\rho \equiv^c_\sigma \rho'$ then $\sigma$ is a consistent
permutation'' (Lemma 17(1)) seems to hold as the original proof do not
to rely on linearity, this should be double-checked, but the converse
is false). In general, the hope is to get rid of using consistent
permutation and use instead more asbtract properties of
shift-equivalence as discussed in the first part.

@@

Relevant technical lemma in UnstableFull are:
